---
title: "ICU Demand Model"
author: "HSO"
date: "6/10/2020"
output: html_document
---

---
title: "ICU Census Scenarios"
author: "HSO"
date: "5/20/2020"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r Install and load packages}
# Code for analyzing historical COVID-19 IP census, admissions, and discharges ----------------------

#Install and load necessary packages --------------------
#install.packages("readraw_dfl")
#install.packages("writeraw_dfl")
#install.packages("ggplot2")
#install.packages("lubridate")
#install.packages("dplyr")
#install.packages("reshape2")
#install.packages("svDialogs")
#install.packages("stringr")
#install.packages("formattable")
# install.packages("ggpubr")
# install.packages("rprojroot")

# Load libraries ------------------------
library(readxl)
library(writexl)
library(ggplot2)
library(lubridate)
library(dplyr)
library(reshape2)
library(svDialogs)
library(stringr)
library(formattable)
library(scales)
library(reshape2)
library(knitr)
library(rmarkdown)
library(kableExtra)

```

```{r Determine drive mapping}
rm(list = ls())

if (list.files("J://") == "Presidents") {
  user_directory <- "J:/Presidents/HSPI-PM/Operations Analytics and Optimization/Projects/System Operations/COVID Scenario Testing"
} else {
  user_directory <- "J:/deans/Presidents/HSPI-PM/Operations Analytics and Optimization/Projects/System Operations/COVID Scenario Testing"
}

```


```{r Import raw data}
# Set working directory and select raw data ----------------------------

covid_trend_start_date <- as.Date("3/12/20", format = "%m/%d/%y")

covid_steady_state_start <- as.Date("5/15/20", format = "%m/%d/%y")
covid_steady_state_end <- as.Date("5/31/20", format = "%m/%d/%y")

sinai_colors <- c("#221f72", "#00AEEF", "#D80B8C", "#4C4D4C", "#8988dd", "#B2B3B2", "#F887CE")

# Import data tables from DataMart ---------------
covid_ip_days_df_raw <- read.csv(paste0(user_directory, "/DataMart/COVID_IP_PATIENT_DAYS_DETAIL_202006091548.csv"), stringsAsFactors = FALSE, na = c("", "NA"))

# Import Epic daily COVID census
epic_covid_census_raw <- read_excel(paste0(user_directory, "/Epic COVID Repo/COVID MRN Daily Census Export 2020-06-08.xlsx"))

# # Import FY2019 IP discharge data
# ip_disch_df_raw <- read_excel(paste0(user_directory, "/IP Discharge Data/IP Disch FY2019 2020-05-13.xlsx"), na = c("", "NA"),
#                                 col_types = c("text", "text", "text", "text", "date", "date", "date",
#                                               "text", "text", "text", "text", "text", "text", "text",
#                                               "numeric", "numeric"))
# 
# # Import FY2019 IP census room & board charge data
# rb_charge_df_raw <- read_excel(paste0(user_directory, "/IP Discharge Data/IP R&B Charges FY2019 2020-05-19.xlsx"))
# 
# # Import analysis reference
# reference_file <- paste0(user_directory, "/IP Discharge Data/Analysis Reference 2020-05-19.xlsx")
# ref_sheets <- excel_sheets(reference_file)
# 
# ref_data <- lapply(ref_sheets, function(x) read_excel(reference_file, sheet = x))
# 
# site_ref <- ref_data[[1]]
# dispo_ref <- ref_data[[2]]
# service_line_ref <- ref_data[[3]]
# units_ref <- ref_data[[4]]

```


```{r Format COVID IP days raw data}
# Format inpatient days dataframe ----------------------------------
dm_covid_days_df <- covid_ip_days_df_raw

# Convert dates from characters to dates
dm_covid_days_df <- dm_covid_days_df %>%
  mutate(CENSUS_DATE = as_datetime(CENSUS_DATE, tz = "America/New_York"),
         ADMIT_DATE = as_datetime(ADMIT_DATE, tz = "America/New_York"),
         DSCH_DATE = as_datetime(DSCH_DATE, tz = "America/New_York"))

# Create columns with census, admit, and discharge dates
dm_covid_days_df <- dm_covid_days_df %>%
  mutate(CensusDate = date(CENSUS_DATE),
         AdmitDate = date(ADMIT_DATE),
         DischDate = date(DSCH_DATE))

# Determine if patient day is an ICU day based on site specific criteria and determine if patient is a COVID patient -----------
# MSQ ICU timeline (provided by A. Dempsey on 5/22/20; updated start date of 3/28/20 provided on 6/1/20)
# 3/28/20-5/6/20:
# 5 East - PACU to ICU - 14 beds
# 6 East - IMCU to ICU - 11 beds
# 6 ICU - ICU - 8 beds

# 5/7/20 - 5/19/20:
# 5 East - back to PACU - 0 beds
# 2 East Rooms 208-217 convert to ICU
# 6 East - IMCU to ICU - 11 beds
# 6 ICU - ICU - 8 beds

# 5/22/20 onward:
# 5 East - back to PACU - 0 beds
# 2 East - back to M/S - 0 beds
# 6 East - 3 IMCU rooms 601, 606, and 608 convert to IMCU - 8 beds
# 6 ICU - ICU - 8 beds

# MSSN: Any bed type defined as critical care or critical care surge
# Other sites: Accommodation code of intensive care or coronary care
# COVID cohort COVID_FLAGS: Positive, PUI, Susc, and Resolved
dm_covid_days_df <- dm_covid_days_df %>%
  mutate(DataMartICUDay = (IP_SITE == "MSSN" & (CENSUS_BED_TYPE %in% "Critical Care" | CENSUS_BED_TYPE %in% "Critical Care Surge")) |
           (IP_SITE != "MSSN" & IP_SITE != "MSQ" & (ACCOMMODATION_DESC %in% "INTENSIVE CARE" | ACCOMMODATION_DESC %in% "CORONARY CARE")) | (IP_SITE == "MSQ" & (CENSUS_DEPT == "MSQ 6 ICU" |
                                                                                                                                                                  (CensusDate >= as.Date("3/28/20", format = "%m/%d/%y") & CensusDate <= as.Date("5/6/20", format = "%m/%d/%y") & CENSUS_DEPT == "MSQ 5 EAST") |
                                                                                                                                                                  (CensusDate >= as.Date("5/7/20", format = "%m/%d/%y") & CensusDate <= as.Date("5/19/20", format = "%m/%d/%y") & CENSUS_DEPT == "MSQ 2 EAST" & CENSUS_ROOM %in% as.character(c(208:217))) |
                                                                                                                                                                  (CensusDate >= as.Date("3/28/20", format = "%m/%d/%y") & CensusDate < as.Date("5/22/20", format = "%m/%d/%y") & CENSUS_DEPT == "MSQ 6 EAST") |
                                                                                                                                                                  (CensusDate >= as.Date("5/22/20", format = "%m/%d/%y") & CENSUS_DEPT == "MSQ 6 EAST" & CENSUS_ROOM %in% as.character(c(601, 606, 608)) == FALSE))),
         
         COVIDPt = (COVID_FLAG %in% c("COVID-POSITIVE", "COVID-PUI", "COVID-SUSC", "COVID-RESOLVED")))


# Subset data frame based on census date and remove MSSN
dm_covid_census_subset <- dm_covid_days_df %>%
  filter(IP_SITE != "MSSN" & COVIDPt & CensusDate >= covid_trend_start_date) %>%
  select(IP_SITE, CSN, MRN, 
         AdmitDate, DischDate, CensusDate, IN_HOUSE, 
         COVID_FLAG, 
         CENSUS_DEPT, CENSUS_ROOM, ACCOMMODATION_DESC, 
         PATIENT_DAY, ICU_DAY, VENT_DAY, VENT_NON_ICU, TOT_CRITICAL_CARE,
         DataMartICUDay, LOAD_DATE, INFECTION_STATUS) %>%
  mutate(DataMartInfection = INFECTION_STATUS)

dm_covid_census_subset$INFECTION_STATUS <- NULL


# # Summarize ICU, vent, critical care, and non-critical care census by day
# ip_covid_daily_census_site <- covid_ip_days_df %>%
#   filter(IP_SITE != "MSSN") %>%
#   group_by(IP_SITE, CensusDate) %>%
#   summarize(IPCOVIDCensus = n(), 
#             ICUCOVIDCensus = sum(ICU), 
#             NonICUVentCensus = sum(VENT_NON_ICU, na.rm = TRUE),
#             CriticalCareCensus = ICUCOVIDCensus + NonICUVentCensus, 
#             NonCriticalCareCensus = IPCOVIDCensus - CriticalCareCensus)
# 
# ip_covid_daily_census_system <- covid_ip_days_df %>%
#   filter(IP_SITE != "MSSN") %>%
#   group_by(CensusDate) %>%
#   summarize(IPCOVIDCensus = n(), 
#             ICUCOVIDCensus = sum(ICU), 
#             NonICUVentCensus = sum(VENT_NON_ICU, na.rm = TRUE),
#             CriticalCareCensus = ICUCOVIDCensus + NonICUVentCensus,
#             NonCriticalCareCensus = IPCOVIDCensus - CriticalCareCensus)
```


```{r Format Epic COVID census data}
epic_covid_census <- epic_covid_census_raw

epic_covid_census <- epic_covid_census %>%
  mutate(Encounter = as.character(PAT_ENC_CSN_ID), 
         EpicInfection = INFECTION_STATUS, 
         CensusDate = date(CENSUS_DATE),
         Site = ifelse(LOC_NAME == "MOUNT SINAI BI BROOKLYN", "MSB",
                       ifelse(LOC_NAME == "THE MOUNT SINAI HOSPITAL" | LOC_NAME == "MS 1160 5TH AVE", "MSH",
                              ifelse(LOC_NAME == "MOUNT SINAI QUEENS HOSPITAL", "MSQ", 
                                     ifelse(LOC_NAME == "MOUNT SINAI WEST", "MSW", 
                                            ifelse(LOC_NAME == "MOUNT SINAI ST. LUKE'S", "MSM", NA))))),
         # Determine if census day was also an ICU day using same logic as above
         EpicICUDay = (Site != "MSQ" & (ACCOMMODATION_CODE %in% "Intensive Care" | ACCOMMODATION_CODE %in% "Coronary Care")) | (Site == "MSQ" & (DEPARTMENT_NAME == "MSQ 6 ICU" |
                                                                                                                                                                  (CensusDate >= as.Date("3/28/20", format = "%m/%d/%y") & CensusDate <= as.Date("5/6/20", format = "%m/%d/%y") & DEPARTMENT_NAME == "MSQ 5 EAST") |
                                                                                                                                                                  (CensusDate >= as.Date("5/7/20", format = "%m/%d/%y") & CensusDate <= as.Date("5/19/20", format = "%m/%d/%y") & DEPARTMENT_NAME == "MSQ 2 EAST" & ROOM_NAME %in% as.character(c(208:217))) |
                                                                                                                                                                  (CensusDate >= as.Date("3/28/20", format = "%m/%d/%y") & CensusDate < as.Date("5/22/20", format = "%m/%d/%y") & DEPARTMENT_NAME == "MSQ 6 EAST") |
                                                                                                                                                                  (CensusDate >= as.Date("5/22/20", format = "%m/%d/%y") & DEPARTMENT_NAME == "MSQ 6 EAST" & ROOM_NAME %in% as.character(c(601, 606, 608)) == FALSE))),
         # Create a flag for COVID census day
         COVIDDay = 1,
         # Determine if census department is an ED or Psych ED to remove later
         ED_Loc = str_detect(DEPARTMENT_NAME, "(EMERGENCY)|(PSYCH ED)"))

# Subset Epic census data to include non-ED locations and selected columns
epic_covid_census_subset <- epic_covid_census %>%
  filter(ED_Loc == FALSE) %>%
  select(Site, MRN, Encounter, CensusDate,
         DEPARTMENT_NAME, EpicInfection, 
         GROUP, `SERVICE GROUPER`, BED_USE, ACCOMMODATION_CODE,
         EpicICUDay, COVIDDay)


```

```{r Crosswalk Epic and DataMart data to pull in ICU and vent logic}
epic_site_covid_crosswalk <- left_join(epic_covid_census_subset, dm_covid_census_subset,
                                    by = c("Encounter" = "CSN", "CensusDate" = "CensusDate"))

# Filter data based on census dates present in Epic and DataMart
epic_site_covid_crosswalk <- epic_site_covid_crosswalk %>%
  filter(CensusDate <= min(max(epic_site_covid_crosswalk$CensusDate),
                           max(dm_covid_census_subset$CensusDate)))

# Determine if census day was a critical care day
epic_site_covid_crosswalk$DataMartICUDay[is.na(epic_site_covid_crosswalk$DataMartICUDay)] <- FALSE

epic_site_covid_crosswalk <- epic_site_covid_crosswalk %>%
  mutate(ICUMaster = ifelse(DataMartICUDay | EpicICUDay, 1, 0),
         CriticalCareDay = ifelse(ICUMaster %in% 1 | VENT_NON_ICU %in% 1, 1, 0))

```

```{r Create MSBI daily census using DataMart}
msbi_covid_census <- dm_covid_census_subset %>%
  filter(IP_SITE == "MSBI" & 
           CensusDate <= min(max(epic_site_covid_crosswalk$CensusDate),
                           max(dm_covid_census_subset$CensusDate)))

# Create a dataframe to mimic Epic crosswalk dataframe
msbi_epic_mimic_covid <- msbi_covid_census %>%
  mutate(Site = "MSBI",
         MRN.x = MRN,
         MRN.y = MRN,
         MRN = NULL,
         Encounter = CSN,
         DEPARTMENT_NAME = NA,
         EpicInfection = NA,
         GROUP = NA,
         `SERVICE GROUPER` = NA,
         BED_USE = NA,
         ACCOMMODATION_CODE = NA,
         EpicICUDay = FALSE,
         COVIDDay = 1,
         ICUMaster = ifelse(DataMartICUDay | EpicICUDay, 1, 0),
         CriticalCareDay = ifelse(ICUMaster %in% 1 | VENT_NON_ICU %in% 1, 1, 0))

epic_col_names <- colnames(epic_site_covid_crosswalk)

msbi_epic_mimic_covid<- msbi_epic_mimic_covid[ , epic_col_names]

```

```{r Combine data for Epic sites and MSBI and create daily census dataframe}
all_sites_covid_enc <- rbind(epic_site_covid_crosswalk, msbi_epic_mimic_covid)

# Create daily COVID census, ICU day, vent days, and critical care days by site
daily_covid_census_site <- all_sites_covid_enc %>%
  group_by(Site, CensusDate) %>%
  summarize(COVIDCensus = n(),
            DMICUCensus = sum(DataMartICUDay, na.rm = TRUE),
            EpicICUCensus = sum(EpicICUDay, na.rm = TRUE), 
            ICUCensus = sum(ICUMaster, na.rm = TRUE), 
            VentNonICUCensus = sum(VENT_NON_ICU, na.rm = TRUE), 
            CriticalCareCensus = sum(CriticalCareDay, na.rm = TRUE)) %>%
  ungroup()

# Create daily COVID census, ICU day, vent days, and critical care days across system
daily_covid_census_system <- all_sites_covid_enc %>%
  group_by(CensusDate) %>%
  summarize(Site = "MSHS",
            COVIDCensus = n(),
            DMICUCensus = sum(DataMartICUDay, na.rm = TRUE),
            EpicICUCensus = sum(EpicICUDay, na.rm = TRUE), 
            ICUCensus = sum(ICUMaster, na.rm = TRUE), 
            VentNonICUCensus = sum(VENT_NON_ICU, na.rm = TRUE), 
            CriticalCareCensus = sum(CriticalCareDay, na.rm = TRUE)) %>%
  ungroup()

daily_covid_census_system <- daily_covid_census_system[ , colnames(daily_covid_census_site)]

# Bind together site and system daily census
daily_covid_census_summary <- rbind(daily_covid_census_site, daily_covid_census_system)



```


```{r Determine dates of peak IP and ICU census}
# Compare ICU census using 2 methods - date with peak IP COVID census and date with peak critical care COVID census

covid_census_peaks <- daily_covid_census_summary %>%
  group_by(Site) %>%
  summarize(PeakIPCensusDate = CensusDate[which.max(COVIDCensus)],
            PeakIPCensus = COVIDCensus[which.max(COVIDCensus)],
            PeakIPICUCensus = ICUCensus[which.max(COVIDCensus)],
            PeakIPVentNonICUCensus = VentNonICUCensus[which.max(COVIDCensus)],
            PeakIPCCCensus = CriticalCareCensus[which.max(COVIDCensus)],
            
            PeakCCCensusDate = CensusDate[which.max(CriticalCareCensus)],
            PeakCCIPCensus = COVIDCensus[which.max(CriticalCareCensus)],
            PeakCCICUCensus = ICUCensus[which.max(CriticalCareCensus)],
            PeakCCVentNonICUCensus = VentNonICUCensus[which.max(CriticalCareCensus)],
            PeakCCCensus = CriticalCareCensus[which.max(CriticalCareCensus)])

site_order <- c("MSH", "MSQ", "MSB", "MSBI", "MSM", "MSW", "MSHS")

covid_census_peaks$Site <- factor(covid_census_peaks$Site, levels = site_order, ordered = TRUE)




```

```{r Determine steady state COVID census}
covid_census_steady_state <- daily_covid_census_summary %>%
  filter(CensusDate >= covid_steady_state_start) %>%
  group_by(Site) %>%
  summarize(AvgIPCensus = mean(COVIDCensus),
            AvgICUCensus = mean(ICUCensus),
            AvgVentNonICUCensus = mean(VentNonICUCensus),
            AvgCriticalCareCensus = mean(CriticalCareCensus))

covid_census_steady_state$Site <- factor(covid_census_steady_state$Site, level = site_order, ordered = TRUE)

```



```{r Format IP discharge data}
# Format inpatient days dataframe ----------------------------------
ip_disch_df <- ip_disch_df_raw

# Create columns with census, admit, and discharge dates
ip_disch_df <- ip_disch_df %>%
  mutate(AdmitDate = date(`Admit Dt Src`),
         DischDate = date(`Dsch Dt Src`),
         AdmitMonth = month(AdmitDate),
         DischMonth = month(DischDate))


# Determine admit source
ip_disch_df <- ip_disch_df %>%
  mutate(AdmitType = ifelse(is.na(`Admit Type Desc Msx`) | str_detect(`Admit Type Desc Msx`, "(INFORMATION NOT AVAILABLE)"), "NonElective",
                            ifelse(str_detect(`Admit Type Desc Msx`, "ELECTIVE"), "Elective",
                            ifelse(str_detect(`Admit Type Desc Msx`, "NEWBORN"), "Newborn",
                                   ifelse(str_detect(`Admit Type Desc Msx`, "(EMERGENCY)|(URGENT)"), "NonElective", "Other")))))

# Crosswalk raw data with reference data -------------------------
# Crosswalk sites
ip_disch_df <- left_join(ip_disch_df, site_ref, by = c("Facility Msx" = "Facility Msx"))

# Crosswalk service lines to include/exclude
ip_disch_df <- left_join(ip_disch_df, service_line_ref[ , c("Service Desc Msx", "ServiceInclude")], by = c("Service Desc Msx" = "Service Desc Msx"))

# If no discharge unit present, set to "Unknown"
ip_disch_df[is.na(ip_disch_df$`Unit Desc Msx`), "Unit Desc Msx"] <- "Unknown"

# Crosswalk unit to determine if it is an ICU, peds unit, nursery/NICU,
ip_disch_df <- left_join(ip_disch_df, units_ref, by = c("Site" = "Site", "Unit Desc Msx" = "Unit Desc Msx"))

```

```{r Susbet data frame based on unit and patient type and then summarize}
# Inclusion criteria
# Remove any peds encounters
# Remove NICU and newborn discharges
# Include any encounter with an ICU LOS > 0 OR any patient discharged from an adult med/surg unit
ip_disch_subset <- ip_disch_df %>%
  filter(PedsUnit == "No" & NurseryNICU == "No" & AdmitType != "Newborn" & (`Icu Days Msx` > 0 | AdultMedSurg == "Yes"))

# Determine total discharges and ICU ADC for each site based on admit type ----------------------------
# Summarize data for each site based on admit type
ip_disch_admit_type_site_level <- ip_disch_subset %>%
  group_by(Site, AdmitType) %>%
  summarize(VolDisch = n(),
            ICUDays = sum(`Icu Days Msx`)) %>%
  ungroup()

# Summarize data for each site across all admit types
ip_disch_all_admits_site <- ip_disch_subset %>%
  group_by(Site) %>%
  summarize(AdmitType = "All",
            VolDisch = n(),
            ICUDays = sum(`Icu Days Msx`)) %>%
  ungroup()

# Bind data together
ip_disch_site_summary <- rbind(ip_disch_admit_type_site_level, ip_disch_all_admits_site)
ip_disch_site_summary <- ip_disch_site_summary[order(ip_disch_site_summary$Site), ]

# Determine total discharges and ICU ADC for system based on admit type -----------------------------
# Summarize data for each site based on admit type
ip_disch_admit_type_system <- ip_disch_subset %>%
  group_by(AdmitType) %>%
  summarize(Site = "MSHS",
            VolDisch = n(),
            ICUDays = sum(`Icu Days Msx`)) %>%
  ungroup()

ip_disch_admit_type_system <- ip_disch_admit_type_system[ , c("Site", "AdmitType", "VolDisch", "ICUDays")]

# Summarize data for each site across all admit types
ip_disch_all_admits_system <- ip_disch_subset %>%
  summarize(Site = "MSHS",
            AdmitType = "All",
            VolDisch = n(),
            ICUDays = sum(`Icu Days Msx`)) %>%
  ungroup()

# Bind data together
ip_disch_system_summary <- rbind(ip_disch_admit_type_system, ip_disch_all_admits_system)

# Calculate ICU ADC for each site and system
ip_disch_site_summary <- ip_disch_site_summary %>%
  mutate(ICUADC = ICUDays / 365)

ip_disch_system_summary <- ip_disch_system_summary %>%
  mutate(ICUADC = ICUDays / 365)

# Bind site and system level data
ip_disch_summary <- rbind(ip_disch_site_summary, ip_disch_system_summary)

# Melt data frame to calculate percentage of elective and non-elective discharges ----------------------
ip_disch_admit_type_percent <- dcast(ip_disch_summary[ , c("Site", "AdmitType", "VolDisch")],
                                  Site ~ AdmitType, value.var = "VolDisch")

ip_disch_admit_type_percent <- ip_disch_admit_type_percent %>%
  mutate(Elective = Elective / All * 100, NonElective = NonElective / All * 100, All = All / All * 100)

ip_disch_admit_type_percent <- melt(ip_disch_admit_type_percent, id.vars = "Site", variable.name = "AdmitType", value.name = "DischPerc")

ip_disch_admit_type_percent$AdmitType <- as.character(ip_disch_admit_type_percent$AdmitType)

# Bind with summary stats table
ip_disch_summary <- left_join(ip_disch_summary, ip_disch_admit_type_percent, by = c("Site" = "Site", "AdmitType" = "AdmitType"))

ip_disch_summary <- ip_disch_summary[ , c("Site", "AdmitType",
                                          "VolDisch", "DischPerc",
                                          "ICUDays", "ICUADC")]


```

```{r Preprocess room and board data to determine daily census}
rb_charge_df <- rb_charge_df_raw

sites_units <- unique(rb_charge_df[ , c("Hospital", "IPD")])

```


```{r Scale historical ICU ADC and COVID IP census data}

# Scale ICU census at peak
# scale_factors <- data.frame("Scale" = c(0.10, 0.20, 0.30, 0.40, 0.50, 0.60, 0.70, 0.8, 0.9, 1.0))
scale_factors <- data.frame("Scale" = c(0.25, 0.5, 0.75, 1.0))

covid_icu_scenarios <- covid_census_icu_peak_summary %>%
  select(IP_SITE, CriticalCareCensus)

ip_icu_scenarios <- ip_disch_summary %>%
  select(Site, ICUADC)

scale_length <- nrow(scale_factors)
covid_icu_length <- nrow(covid_icu_scenarios)
ip_icu_length <- nrow(ip_icu_scenarios)

# Replicate data frames
scale_factors_covid <- (scale_factors[rep(rownames(scale_factors), covid_icu_length), ])
scale_factors_covid <- data.frame("Scale" = scale_factors_covid)

scale_factors_ip_icu <- (scale_factors[rep(rownames(scale_factors), ip_icu_length), ])
scale_factors_ip_icu <- data.frame("Scale" = scale_factors_ip_icu)

scale_factors_covid <- scale_factors_covid[order(scale_factors_covid$Scale), ]
scale_factors_ip_icu <- scale_factors_ip_icu[order(scale_factors_ip_icu$Scale), ]

covid_icu_scenarios <- covid_icu_scenarios[rep(rownames(covid_icu_scenarios), scale_length), ]
covid_icu_scenarios = cbind(covid_icu_scenarios, Scale = scale_factors_covid)

ip_icu_scenarios <- ip_icu_scenarios[rep(rownames(ip_icu_scenarios), scale_length), ]
ip_icu_scenarios = cbind(ip_icu_scenarios, Scale = scale_factors_ip_icu)

# Calculate census for different scenarios based on historical data and scale
covid_icu_scenarios <- covid_icu_scenarios %>%
  mutate(ScaledICUCensus = CriticalCareCensus * Scale,
         ScaleName = paste0(Scale*100, "% Peak"))

ip_icu_scenarios <- ip_icu_scenarios %>%
  mutate(ScaledICUCensus = ICUADC * Scale,
         ScaleName = paste0(Scale*100, "% Historical"))

# Set site and scale name to factors before casting
covid_icu_scenarios$IP_SITE <- factor(covid_icu_scenarios$IP_SITE, levels = c("MSH", "MSQ", "MSB", "MSBI", "MSW", "MSM", "MSHS"), ordered = TRUE)

covid_icu_scenarios$ScaleName <- factor(covid_icu_scenarios$ScaleName,
                                   levels = c("25% Peak", "50% Peak", "75% Peak", "100% Peak"), ordered = TRUE)

ip_icu_scenarios$Site <- factor(ip_icu_scenarios$Site, levels = c("MSH", "MSQ", "MSB", "MSBI", "MSW", "MSM", "MSHS"), ordered = TRUE)

ip_icu_scenarios$ScaleName <- factor(ip_icu_scenarios$ScaleName,
                                   levels = c("25% Historical", "50% Historical", "75% Historical", "100% Historical"), ordered = TRUE)

# Cast data frame for kables
covid_icu_scenarios_cast <-  dcast(covid_icu_scenarios, IP_SITE + CriticalCareCensus ~ ScaleName, value.var = "ScaledICUCensus")
covid_icu_scenarios_cast$IP_SITE <- as.character(covid_icu_scenarios_cast$IP_SITE)

ip_icu_scenarios_cast <-  dcast(ip_icu_scenarios, Site + ICUADC ~ ScaleName, value.var = "ScaledICUCensus")
ip_icu_scenarios_cast$Site <- as.character(ip_icu_scenarios_cast$Site)


# Bind COVID scenarios with COVID census peak summary table
covid_census_peak_summary_scenarios <- left_join(covid_census_icu_peak_summary[ , c("IP_SITE", "ICUPeakDate", "IPCensus", "ICUCensus", "NonICUVentCensus", "CriticalCareCensus")], covid_icu_scenarios_cast, by = c("IP_SITE" = "IP_SITE", "CriticalCareCensus" = "CriticalCareCensus"))

# Bind ICU ADC scenarios with IP discharge summary table
ip_disch_summary_scenarios <- left_join(ip_disch_summary, ip_icu_scenarios_cast, by = c("Site" = "Site", "ICUADC" = "ICUADC"))

```

```{r Custom function for creating IP ICU projection table}
icu_census_project <- function(site) {
  site <- site

  ip_icu_scenarios_site <- ip_disch_summary_scenarios %>%
    filter(Site == site)

  ip_icu_scenarios_site$Site <- NULL

  kable(ip_icu_scenarios_site, format = "html", escape = FALSE, align = "c", digits = 1,
      col.names =c("Admit Type", "# Discharges", "% Discharges", "ICU Days", "ICU ADC",
                   "25% Historical", "50% Historical", "75% Historical", "100% Historical"),
      caption = paste(site, " ICU Census Scenarios (Based on FY2019 Data)")) %>%
  kable_styling(bootstrap_options = "hover", position = "center", font_size = 11, full_width = FALSE) %>%
  column_spec(column = c(1, 5), border_right = "thin solid lightgray") %>%
  column_spec(column = c(2:5), background = sinai_colors[1], color = "white", include_thead =  TRUE) %>%
  column_spec(column = c(6:9), background = sinai_colors[2], color = "white", include_thead =  TRUE) %>%
  column_spec(column = c(2:9), background = "inherit", color = "inherit") %>%  
  # row_spec(row = 0, background = "#221f72", color = "white") %>%
  row_spec(row = nrow(ip_icu_scenarios_site), background = "lightgrey", bold = T) %>%
  add_header_above(c(" " = 1, "FY2019 Discharges" = 4, "ICU Census Scenarios" = 4), background = c("", sinai_colors[1], sinai_colors[2]), color = "white", line = FALSE)

}


```

```{r Custom function for creating COVID-19 steady state census table}
covid_steady_state_census <- function(site) {
  site <- site

  covid_stead_state_census <- covid_census_steady_state_summary %>%
    filter(IP_SITE == site)

  covid_stead_state_census$IP_SITE <- NULL

  kable(covid_stead_state_census, format = "html", escape = FALSE, align = "c", digits = 1,
      col.names =c("IP Census", "ICU Census", "Non-ICU Vent Census", "Critical Care Census"),
      caption = paste(site, " COVID-19 Steady State Census (Average of 05/15/20-Present)")) %>%
  kable_styling(bootstrap_options = "hover", position = "center", font_size = 11, full_width = FALSE) %>%
  column_spec(column = c(1, 3), border_right = "thin solid lightgray") %>%
  column_spec(column = c(1:4), background = sinai_colors[1], color = "white", include_thead =  TRUE) %>%
  column_spec(column = c(1:4), background = "inherit", color = "inherit") %>%
  # row_spec(row = 0, background = "#221f72", color = "white") %>%
  add_header_above(c("COVID-19 Average Census" = 4), background = sinai_colors[1], color = "white", line = FALSE)
}


```

```{r Custom function for creating COVID-19 projection table}
covid_census_project <- function(site) {
  site <- site

  covid_disch_scenarios_site <- covid_census_peak_summary_scenarios %>%
    filter(IP_SITE == site)

  covid_disch_scenarios_site$IP_SITE <- NULL

  kable(covid_disch_scenarios_site, format = "html", escape = FALSE, align = "c", digits = 1,
      col.names =c("Date", "IP Census", "ICU Census", "Non-ICU Vent Census", "Critical Care Census",
                   "25% Peak", "50% Peak", "75% Peak", "100% Peak"),
      caption = paste(site, " COVID-19 ICU Census Scenarios")) %>%
  kable_styling(bootstrap_options = "hover", position = "center", font_size = 11, full_width = FALSE) %>%
  column_spec(column = c(1, 5), border_right = "thin solid lightgray") %>%
  column_spec(column = c(1:5), background = sinai_colors[1], color = "white", include_thead =  TRUE) %>%
  column_spec(column = c(6:9), background = sinai_colors[2], color = "white", include_thead =  TRUE) %>%
  column_spec(column = c(1:9), background = "inherit", color = "inherit") %>%
  # row_spec(row = 0, background = "#221f72", color = "white") %>%
  add_header_above(c("COVID-19 Peak ICU Census" = 5, "COVID-19 Critical Care Census Scenarios" = 4), background = c(sinai_colors[1], sinai_colors[2]), color = "white", line = FALSE)
}


```

## ICU Census Comparison
Two methods implemented to determine peak ICU census for scenario testing:

* Method 1: Utilize ICU census from date with highest COVID-19 IP census
* Method 2: Utilize ICU census from date with highest COVID-19 ICU census
```{r Create kable comparing two methods of calculating peak ICU census}
kable(compare_covid_peak_summary, format = "html", escape = FALSE, align = "c", 
      col.names = c("Site", "Date", "IP Census", "ICU Census", "Date", "IP Census", "ICU Census"),
      caption = "ICU Census Methodology Comparison") %>%
  kable_styling(bootstrap_options = "hover", position = "center", font_size = 11, full_width = FALSE) %>%
  column_spec(column = c(1, 4), border_right = "thin solid lightgray") %>%
  column_spec(column = c(2:4), background = sinai_colors[1], color = "white", include_thead =  TRUE) %>%
  column_spec(column = c(5:7), background = sinai_colors[2], color = "white", include_thead =  TRUE) %>%
  column_spec(column = c(2:7), background = "inherit", color = "inherit") %>%
  # row_spec(row = 0, background = "#221f72", color = "white") %>%
  row_spec(row = nrow(compare_covid_peak_summary), background = "lightgrey", bold = T) %>%
  add_header_above(c("Site" = 1, "Method 1: Peak COVID-19 IP Census" = 3, "Method 2: Peak COVID-19 ICU Census" = 3), background = c("", sinai_colors[1], sinai_colors[2]), color = "white", line = FALSE)

```
**Method 2 provides more conservative ICU projections and will be used moving forward.**

## ICU Census Projections
### MSHS
*Excludes MSSN*
```{r Create tables for MSHS}
icu_census_project(site = "MSHS")

covid_steady_state_census(site = "MSHS")

covid_census_project(site = "MSHS")

```


### MSH
```{r Create tables for MSH}
icu_census_project(site = "MSH")

covid_steady_state_census(site = "MSH")

covid_census_project(site = "MSH")

```

### MSQ
```{r Create tables for MSQ}
icu_census_project(site = "MSQ")

covid_steady_state_census(site = "MSQ")

covid_census_project(site = "MSQ")

```

### MSB
```{r Create tables for MSB}
icu_census_project(site = "MSB")

covid_steady_state_census(site = "MSB")

covid_census_project(site = "MSB")

```

### MSBI
```{r Create tables for MSBI}
icu_census_project(site = "MSBI")

covid_steady_state_census(site = "MSBI")

covid_census_project(site = "MSBI")

```

### MSM
```{r Create tables for MSM}
icu_census_project(site = "MSM")

covid_steady_state_census(site = "MSM")

covid_census_project(site = "MSM")

```

### MSW
```{r Create tables for MSW}
icu_census_project(site = "MSW")

covid_steady_state_census(site = "MSW")

covid_census_project(site = "MSW")

```

## Data Sources and Methodology
**Historical ICU Census Analysis:**</br>
**Data Source:** FY2019 ICU ADC based on billing data for patients discharged from 1/1/2019-12/31/2019.</br>
Elective and non-elective breakdown based on encounter admit type.</br>
Analysis exclusions:

* All encounters discharged from peds, nursery, and NICU.
* All encounters discharged from psych, rehab, mother-baby, and chemical dependency units unless the patient spent 1 or more days in an ICU.

**COVID-19 Census:**</br>
**Data Source:** COVID patient registry maintained in Enterprise Data Mart using inpatient tables. Data pulled on 5/12/2020 10:20AM.</br>
Analysis includes patients with COVID flags of COVID-POSITIVE, COVID-PUI, COVID-SUSC, and COVID-RESOLVED.</br>
*ICU classifications:*</br>
MSH, MSB, MSW, MSM, MSBI: Accommodation type of Intensive Care or Coronary Care.</br>
MSQ: Based on unit and bed history described below.</br>

* MSQ 6 ICU: Always ICU
* MSQ 5 East: PACU converted to ICU prior to 5/7/20
* MSQ 6 East: ICU prior to 5/22/20 when rooms 601, 606, and 608 converted back to IMCU
* MSQ 2 East: Rooms 208-217 converted to ICU from 5/7/20-5/19/20




